Analysis

### 2025-01-18 production/prod_analysis-fix-t5.Rmd
reorder vars
ajusta citations keys
ajusta n descriptivos
cambia orden tabla multinivel
render paper

# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

@@

# Df variables nivel 1 _________________________________________________________
df_study1 <- df_study_long_t7_comunas %>% dplyr::select(ola, idencuesta,
                                               just_educ, covid_economia, covid_beneficios, des_perc, merit_talent, merit_effort,
                                               educ, ing_pc, ess:sexo)
colSums(is.na(df_study1))

@@

df_study1$ola <- factor(df_study1$ola,
         labels = c("2016","2017","2018","2019", "2022", "2023"))
df_study1$ola <- 
sjlabelled::set_label(x = df_study1$ola,
                      label = "Wave")

@@

@@

df<- dfSummary(x = dplyr::select(df_study1, ola, covid_economia, covid_beneficios, merit_talent, merit_effort, des_perc, educ, ing_pc, ess, edad, sexo, pos_id),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = F, # n valido
               col.widths = c(700,10,10,10)
               )
df$Variable <- NULL # delete variable column
summarytools::view(df,
     file = here::here("output/tables/desc02.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc02.html"),
        file =here::here("output/tables/desc02.png")) # Remover archivo HTML
# print(df, method = "render")
```

@@

ggsave(alluvial_justeduc, file="output/graphs/alluvial_dep.png", height = 8, width = 7)
```

@@

```{r cor-plot, fig.dim=c(12,7)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               sjPlot,
               sjmisc,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t7_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, covid_economia, covid_beneficios, merit_talent, merit_effort, des_perc, 
                                               educ, ing_pc, ess, edad, sexo, pos_id) %>% na.omit()
# Full sample_______________________________________________________________________
mat_full<- 
df_study1 %>%
  # filter(ola==1) %>%
  select(just_educ, # distributive justice
         des_perc,
         merit_effort, merit_talent # meritocracy
         ) %>% 
  psych::mixedCor()

@@

                        "B. Inequality perception",
                     "C. People are rewarded for their efforts",
                     "D. People are rewarded for their intelligence")

@@

colnames(cor_full) <-c("(A)", "(B)","(C)","(D)")

@@

png("output/graphs/corr.png",width=700,height=600, pointsize = 10)

@@

grid::grid.text("Source: own elaboration with pooled data 
from ELSOC 2016-2023 (n = 7576)", x = 0.01, y = 0.05, just = "left", gp = grid::gpar(fontsize = 10, col = "black"))

>>>>

# Css
st_css()
st_options(lang = "en",
           footnote = "Note: Descriptives presented only for wave 1",
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

@@

# Df variables nivel 1 _________________________________________________________
df_study1 <- df_study_long_t7_comunas %>% 
  dplyr::select(ola, idencuesta,
                just_educ, covid_economia, covid_beneficios, des_perc, merit_talent, merit_effort,
                educ, ing_pc, ess:sexo) %>% 
  filter(ola==1)
colSums(is.na(df_study1))

@@

# df_study1$ola <- factor(df_study1$ola,
#          labels = c("2016","2017","2018","2019", "2022", "2023"))
# df_study1$ola <- 
# sjlabelled::set_label(x = df_study1$ola,
#                       label = "Wave")

@@

df_study1$ess <- 
sjlabelled::set_label(x = df_study1$ess, 
                      label = "Subjective social status")

df_study1$ing_pc <- 
sjlabelled::set_label(x = df_study1$ing_pc, 
                      label = "Household income per capita")

@@

df<- dfSummary(x = dplyr::select(df_study1, covid_economia, covid_beneficios, 
                                 merit_talent, merit_effort, des_perc, 
                                 educ, ing_pc, ess, edad, sexo, pos_id),
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = F, # n valido
               col.widths = c(700,10,10,10)
               )
df$Variable <- NULL # delete variable column
summarytools::view(df,
     file = here::here("output/tables/desc02.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc02.html"),
        file =here::here("output/tables/desc02.png")) # Remover archivo HTML
# print(df, method = "render")
```

@@

ggsave(alluvial_justeduc, file="output/graphs/alluvial_dep.png", height = 7, width = 9)
```

@@

```{r cor-plot, fig.dim=c(12,7)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               sjPlot,
               sjmisc,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t7_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, covid_economia, covid_beneficios, merit_talent, merit_effort, des_perc, 
                                               educ, ing_pc, ess, edad, sexo, pos_id) %>% na.omit()
# Full sample______________________________________________________________________
mat_full<- 
df_study1 %>%
   filter(ola==1) %>%
  select(just_educ, # distributive justice
         covid_economia,
         covid_beneficios,
         des_perc,
         merit_effort, merit_talent # meritocracy
         ) %>% 
  psych::mixedCor()

@@

                        "B. Economy more important than health",
                        "C. Receive state benefits",
                        "D. Inequality perception",
                     "E. People are rewarded for their efforts",
                     "F. People are rewarded for their intelligence")

@@

colnames(cor_full) <-c("(A)", "(B)","(C)","(D)", "(E)", "(F)")

@@

png("output/graphs/corr.png",width=700,height=600, pointsize = 12)

@@

grid::grid.text("Source: own elaboration with data 
from ELSOC 2016 (n = 1322)", x = 0.01, y = 0.05, just = "left", gp = grid::gpar(fontsize = 12, col = "black"))
